---
title: "DataSalary"
author: "Kazuki"
date: "2024-09-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Loading Dataset

```{r dataset}
myData = read.csv("Test.csv")
```

## Converting character to double

First I need to convert the Salary in Rupees column from characters to a double. R cannot make histograms of columns that are not numeric.
```{r convert}
myData$Salary_In_Rupees = as.numeric(gsub(",","", myData$Salary_In_Rupees))
```

## Histogram
Salary in Rupees will be the column I choose for the histogram to see the distribution of salaries.The graph seems to imply that most of the salaries are on the lower end.
```{r}
hist(myData$Salary_In_Rupees, main = "Histogram of Salaries in Rupees", xlab="Salary in Rupees", ylab = "Frequency")
```
## Scatter plot
I will check if remote working ratio and salary in rupees have a correlation between each other. There is no apparent correlation.

```{r scatter plot}
library(ggplot2)
ggplot(myData,aes(x=Remote_Working_Ratio,y=Salary_In_Rupees))+ geom_point(color = "black")
+
  labs(title = " Remote Working Ratio vs Salary In Rupees", x = "Remote Working Ratio", y = "Salary in Rupees")
```

