---
title: "DataSalary"
author: "Kazuki"
date: "2024-09-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Loading Dataset

```{r dataset}
myData = read.csv("Test.csv")
```

## Converting character to double

First I need to convert the Salary in Rupees column from characters to a double. R cannot make histograms of columns that are not numeric.
```{r convert}
myData$Salary_In_Rupees = as.numeric(gsub(",","", myData$Salary_In_Rupees))
```

## Histogram
Salary in Rupees will be the column I choose for the histogram to see the distribution of salaries.The graph seems to imply that most of the salaries are on the lower end.
```{r}
hist(myData$Salary_In_Rupees, main = "Histogram of Salaries in Rupees", xlab="Salary in Rupees", ylab = "Frequency")
```
## Scatter plot
I will check if remote working ratio and salary in rupees have a correlation between each other. There is no apparent correlation.

```{r scatter plot}
library(ggplot2)
ggplot(myData,aes(x=Remote_Working_Ratio,y=Salary_In_Rupees)) + 
  geom_point(color = "black")+
  labs(title = " Remote Working Ratio vs Salary In Rupees", x = "Remote Working Ratio", y = "Salary in Rupees")
```

#Calculations
I will use the average salary calculated as a standard for comparing salaries in different locations.
```{r}
mean(myData$Salary_In_Rupees)
```

# Regression
The regression test oddly enough seems to imply there is a positive correlation since the line is rising as the remote working ratio increases. It could mean that people who work more remotely get paid more.
```{r}
library(ggplot2)
ggplot(myData,aes(x=Remote_Working_Ratio,y=Salary_In_Rupees)) + 
  geom_point(color = "black")+
   geom_smooth(method = "lm", se = FALSE, color = "blue")+
  labs(title = " Remote Working Ratio vs Salary In Rupees", x = "Remote Working Ratio", y = "Salary in Rupees")

```
# T Test
I would like to see if Japan pays out better than other countries, so I will compare the salary entries in all countries besides Japan and all entries including Japan. There are much fewer entries than I imagine and based on the P value, we fail to reject the null hypothesis. We cannot support the hypothesis that japan pays out better than other countries.
```{r}
japan = subset(myData, Company_Location=="JP")
notJapan = subset(myData, Company_Location!="JP")
test_result = t.test(japan$Salary_In_Rupees, notJapan$Salary_In_Rupees)
print(test_result)
```
